\documentclass[a4paper, 11pt]{article}

\input{../global-preamble.tex}

% \usepackage{draftwatermark}
% \SetWatermarkText{\textcolor{red!10}{DRAFT}}
% \SetWatermarkScale{2}


\begin{document}
\bookTitle{Under 18 Volunteer Pricing Policy}{A guide to being aged 16 or 17 and volunteering at Venturer Camp}{4th March 2023}{under-18-vol-pricing}
\section{Introduction}
\subsection{Participants \& Volunteers}
Venturer Camp 2023 has expanded age ranges to include anyone aged 13-17 inclusive as a participant, this is due to the Covid Pandemic. By default, anyone attending the camp who is aged under 18 will be classified as a participant and charged the participant fee; and those who are aged 18 and above will be attending the camp as a volunteer and they will be charged the volunteer fee.\\

There is an option for young people aged 16 or 17 to become a volunteer and be charged the volunteer fee. This document will outline the the process to do this and requirements of this.\\

Regardless of if a person aged under 18 is attending Venturer Camp as a participant or volunteer, they are still a child according to law and therefore Woodcraft Folk's safeguarding policy \& procedures. The Venturer Camp coordination team recognise this and that there will be a difference in the expectations of a 16 or 17 year old volunteer and a volunteer aged over 18. 

\subsection{Volunteer Pricing}
Volunteers are being charged a reduced rate as part of Woodcraft Folk's commitment to reduce barriers to volunteering. The Venturer Camp coordination team recognises that camp programme is targeted at 13-17 years, and as such there is no dedicated programme for over 18s. The Venturer Camp coordination team have decided to charge volunteers a reduced fee to recognise their contribution, without which the camp would be unable to happen.\\

The Venturer Camp coordination team recognises that anyone coming to the camp may experience financial barriers, as such an access fund will be launched in April 2023. 

\subsection{Participant Voluntary Contribution}
Participants of the camp will still be expected to undertake standard camping tasks, as is expected at Woodcraft Folk Events as part of the cooperative nature of the organisation. 

\section{Who Is Eligible?}
\subsection{Different Voluntary Commitments}
The Venturer Camp coordination team recognises that there are different voluntary roles, each with different commitments before, during and after camp. The coordination team does not wish to display favouritism for one team of volunteers over another as all volunteers are equally as important in making the camp a success.

\subsection{Role Requirements}
Anyone aged under 16 or 17 is eligible for a reduced price place at camp, if they are taking on a \textit{significant} voluntary role. A voluntary role is classed as significant when:
\begin{itemize}
    \item the role is the persons primary focus on site; and
    \item the role will require the majority of the persons time on site for at least 5 full days of camp (or 70 \% of their time on site if they are not on site for the whole event);
\end{itemize}

\section{Applying For A Reduced Price Place}
\subsection{Prerequisites For Application}
Before an application can be placed, there are a number of prerequisites. These will be checked on submission of an application and the application will be rejected if any of these criteria are not satisfied.\\

The young person must: 
\begin{enumerate}
    \item have begun the process of obtaining a Enhanced DBS (or membership of the PVG scheme if based in Scotland);
    \item be registered as a member of Woodcraft Folk and have paid their membership fee;
    \item have submitted references (this will normally have been done as part of becoming a member of Woodcraft Folk); and
    \item have spoken to the relevant team leader about the role and a volunteer role description has been produced (this should be included with the application). 
\end{enumerate}

\subsection{The Application}
Assigning an under 18 year old a volunteer priced place is at the discretion of the Camp Coordinator \& relevant team leader. Applications should be sent to \href{mailto:info@venturercamp.org.uk}{\texttt{info@venturercamp.org.uk}} at the time of applying to book or booking, should it be part of a larger booking.

\subsection{Outcome Of The Application}
The decision will be communicated via email to the booking contact \& applicant, and the price reduction will be manually entered on the booking system. The booking contact will be able to login to the booking system to view the updated invoice. 

\section{On-Site Practicalities}
\subsection{Safeguarding}
For Safeguarding purposes, the young person will still require a designated leader. The volunteering young person will still count as a young person in the ratio of adults to young people.

\subsection{Wristbands}
Young people taking on voluntary roles will be given a different wristband to those over-18 and participants. This is to recognise the difference between them and an over-18 volunteer.

\subsection{Volunteering Hours}
Volunteers aged 16 or 17 may also have some restrictions on when they can volunteer on site (for example, volunteers aged under 18 will not be allowed to be on overnight stewarding shifts or be alone on stewarding shifts). 

\backPage
\end{document}