\chapter{Introduction}

Welcome to the Booking Handbook, a guide to the booking process for Venturer Camp 2023!

\section{Booking System}
We are using a modified version of the Common Ground booking system. Information on how to access the booking system and how to use it are available in the subsequent sections of this handbook.

\section{Support}
If you need support with the booking process or have any questions which aren't answered on our \href{https://venturercamp.org.uk/book}{FAQs}, drop us an email to \href{mailto:info@venturercamp.org.uk}{\texttt{info@venturercamp.org.uk}}.

\section{Overview of Booking Process}
The booking process has a number of parts.
\begin{enumerate}
    \item Apply to book (section \ref*{chap:apply})
    \item Book (section \ref*{chap:book})
    \item Edit booking (section \ref*{chap:edit})
\end{enumerate}

\section{Individual Bookings}
Where possible, you should book as part of a group. If you are an individual who is planning to camp with a group you are part of or affiliated with, please get in contact with them to be included in their booking. 

\section{Membership \& DBS}
Everyone over the age of 16 will need to be a member of Woodcraft Folk. Information on how to become a member can be found on the \href{https://woodcraft.org.uk/group-guidance/support-advice/membership/}{Woodcraft Website}.

Anyone over the age of 16 taking on a role in which they are responsible for under 16 year olds and everyone over the age of 18 will need to have completed a DBS/ PVG check. Information on how to do this will be available through your local Membership Secretary or through the \href{https://woodcraft.org.uk/resources/volunteer-screening/}{Woodcraft Website}.

Further information on Safeguarding at Venturer Camp 2023 will be made available on our dedicated \href{https://venturercamp.org.uk/safeguarding}{safeguarding webpage}.