\chapter{Coordinator's Introduction}

Welcome to the Venturer Camp 2023 Final Report \& Evaluation.\\

For the most part, this document has been co-authored by the entire Venturer Camp team, with the Coordinator and Woodcraft Folk Events Assistant producing the first draft. This section, however, has solely been written by me - Thomas Boxall, Camp Coordinator.\\

To coordinate such a big Woodcraft Event was a great privilege. I grew up as a young person in Woodcraft and after seeing the impact the Covid Pandemic has had on the young people of today, I'm honoured to be able to say that I've changed these young people's lives by giving them a space where they can be themselves, have fun, forget the pressures of the outside world and take part in workshops centred around Woodcraft Folk's values.\\

However, saying that the year which we made Venturer Camp happen in was an easy one - would be a lie. Just saying it was a difficult one would also be a lie. The year from August 2022 to August 2023 was probably one of the most challenging years I've had in my life, due to a number of things - my role in coordinating Venturer Camp being one of them. \\

Woodcraft Folk is really great at empowering young people to do things, look at me - I was 19 while coordinating this thing. However, it's not good at supporting them to do big scary things like this. To say the year I was coordinating Venturer Camp was tough on my mental health would be an understatement. I'm extremely grateful for those around me who were able to catch me when I fell, both in and out of Woodcraft. They were the reason I was able to coordinate the camp. You know who you are - thank you for that.\\

Saying this, Woodcraft is good at catching people. From speaking to teams while writing this evaluation - I wasn't the only one to struggle with the work. Many of the teams had more and more work piled onto them, or individual members within teams who initially agreed to take on a small role ended up being instrumental in the success of that team's work. Through all the ever-increasing workloads, teams pulled it off. They more than pulled it off, they did it so well that we didn't notice how well they did it - the ultimate sign of success when it all goes smoothly.\\

Why Woodcrafter's have to fall before they can be supported is something that we need to consider, as an organisation. We cannot leave this untouched if we want to be a sustainable organisation which supports its members to try new things.\\

Pulling an event like Venturer Camp 2023 together in 365 days is by no means an easy feat. The countless hours of dedication from Volunteers up and down the country were the reason 450 people were able to be together in a field for 7 days and mostly have a good time. The majority of the work required to pull this event together fell to a relatively small group of active volunteers. Whilst it may seem from the outside that we had a substantial number of volunteers involved in the project, many of these weren't able to commit to a large role leaving a small core team to do most of the work. Throughout this report, you'll hear about different teams' struggles with capacity and workload management. Every core team member should be commended for how well they managed, how well they coped with the ever-increasing workload and how well they rose to the challenge of pulling off a Venturer Camp in a year. Don't ever try and do it in a year again, it's a silly idea.\\

I'm extremely proud of everyone who had a part to play in the success of Venturer Camp, all those who contributed countless hours making meticulous spreadsheets; those who contacted suppliers and chased to get the cheapest and best meatballs they could; those who cleaned the toilets and showers; and especially those who turned up, tried something new and had fun. We wouldn't have done this without you - thank you for that.\\

I want to leave you to enjoy the rest of this evaluation with a quote: ``we do this because we love Woodcraft''.\\

Blue skies,\\

Thomas Boxall\\

Venturer Camp 2023 Coordinator\\
<thomas@woodcraft.org.uk>
