\chapter{Introduction to the Evaluation}
This Final Report \& Evaluation of Venturer Camp 2023 has been primarily compiled by Thomas Boxall, Venturer Camp 2023 Coordinator (Volunteer), and Millie Burgh, Woodcraft Folk Events Assistant (Staff).\\

Every effort has been made to ensure that this report is as accurate and representative of all teams as possible. However, there may be times where this was not possible. All data referenced throughout this evaluation is available on request. Please contact the Camp Coordinator should you have any questions or wish to seek clarification on anything.

\section{Methods Used}
Opinions and Thoughts from the wider coordination team were gathered through a series of interviews conducted by the Camp Coordinator and Events Assistant. \\

Feedback from participants was gathered during the event itself through a Workshop run on a village level. Not all villages submitted notes from their workshop, so participant evaluations may not be representative of all participants on site. \\

All Volunteers involved in the project were invited to complete a Google Forms questionnaire after camp where they could give feedback. As expected with a survey like this, not all volunteers have responded and those who have responded would fall at either end of the spectrum, either having lots of good things to say or lots of bad things. Conversations had with volunteers throughout the event have been included.
\begin{figure}[h]
    \centering
    \begin{tikzpicture}
        \pie[text=pin]{33.3/Group Leaders,
        20.83/Programme Volunteers,
        12.5/Central Food Team,
        8.33/Village Coordinators,
        8.33/Village KPs,
        8.33/Village Safeguarding Leads,
        4.19/Steward,
        4.19/Didn't answer
        }
    \end{tikzpicture}
    \caption{Respondents to the Google Form Questionnaire}
    
\end{figure}

\section{Why Such A Long Evaluation?}
To put it simply, we should be evaluating our projects like this properly. Big camps are such a fundamental part of Woodcraft Folk's operations and with the organisation nearing its 100th birthday, you'd think we've got pretty good at getting lots of Woodcrafters in a field together having a good time. This is only mostly true, however.\\

This report aims to cover what we did, how we did it, and why we did it. As well as if it worked, how people found it and what we'd do differently in the future. \\

In all reality, there's going to be very few people who read the entirety of this document from cover to cover. However, people taking on roles at future large camps should be encouraged to read the sections relevant to them. 

\section{Photo Credits}
Photos have been used throughout this report, the captions include the initials of the photogropher, see below for names of those photographers:
\begin{description}
    \item[AB] Alex Baird
    \item[IC] Isabel Cleveland
    \item[RS] Ralph Sleigh
    \item[TB] Thomas Boxall
\end{description}

\section{Contact Information of Those Mentioned}
Due to this report being made available to the public on the internet, contact information of most people involved in this project has been redacted. The exceptions to this are Woodcraft Folk members of staff and the Camp Coordinator.\\

To obtain the contact information of anyone mentioned in the report - please contact Thomas Boxall, Camp Coordinator via \href{mailto:thomas@woodcraft.org.uk}{thomas@woodcraft.org.uk}
