\chapter{Extra Stakeholders \&  Volunteers}
\section{Venturer Committee}
At the time of project kick-off for this event - there was no functioning Venturer Committee. This was due to the pandemic and the fact that all the current members had `aged-out'. This led to there being very little involvement in the planning process from Venturer aged people. It was an unfortunate loss to not have young people's voices on the planning committee. We had hoped to overcome this shortfall with a scheme called the \textit{Village People}

In September 2022, a meeting was held between key individuals where it was discussed about using Venturer Camp as a chance to re-form Venturer Committee. Due to a combination of factors, including lack of capacity in progressing with re-forming Venturer Committee, nothing happened with this until camp itself started.

On Camp, an individual planned and held Venturer Committee elections with the support of previous Facilitators. The elections held at the event were a great success and all roles on Venturer Committee were able to be filled. This individual also held other roles of responsibility on camp, and as such they had a very busy time. For future events, it would be recommended that an individual with no other commitments takes on the Venturer Committee Elections Facilitation role.

\section{Village People}
The Village People was a scheme designed to introduce the voice of the participants and the people who knew the participants the best into the planning of Venturer Camp 2023. In Autumn 2022, we invited all Venturer Leaders to apply to join the group. We then selected a representative sample, ensuring all types \& sizes of groups were represented.\\

The scheme unfortunately died out quite quickly due to extremely low response rates to opinion-gathering forms which went out. It would be lovely to see a scheme like this work at a future large Woodcraft Camp. 

\section{International Volunteers}
After Brexit, organisations in the UK are no longer eligible to participate in the European Solidarity Corps (ESC) programme run by the European Commission. Common Ground (2022 International Camp) was supported by a 15-strong team of ESC volunteers and as such, it was hoped that Venturer Camp 2023 would also be able to be supported by a number of international volunteers as those at Common Ground proved extremely valuable to the team.\\

Woodcraft Folk worked with a UK-based charity called Concordia to manage the recruitment of volunteers. A further evaluation of how this worked, what went well and what didn't work can be found in the Concordia chapter.
