\chapter{Booking Timelines}
Once we had decided on dates for the camp, we could begin to work backwards designing timelines to suit. We settled on the public timeline shown in Table \ref{tab:booking-public-timeline}

\begin{table}[h]
    \centering
    {\RaggedRight
    \begin{tabular}{p{0.3\textwidth} p{0.5\textwidth}}
    \textbf{Date} & \textbf{Event}\\
    \hline
    \hline
    27 January 2023 & Bookings Open\\
    \hline
    12 April 2023 & Early Bird Booking Deadline\\
    \hline
    26 May 2023 & Final Booking Deadline\\
    \hline
    \end{tabular}
    } % end of rr     
    \caption{Public Booking Timeline}
    \label{tab:booking-public-timeline}
\end{table}

As we were designing the booking timeline, we made the decision to not close bookings. We believed that if we were to fully close bookings then we would be at risk of people turning up to camp who hadn't booked and would want to book on the door, or worse - they wouldn't tell the camp coordination team they had arrived which would complicate number based operations, such as food distribution or village size. We made a conscious decision to brand the 26 May 2023 deadline as the ``Final Booking Deadline'' in hope that we would deter people from booking late, and for the most part, we did.\\

We also had a second timeline, this was created and was published in the Payment Policy for Individuals and Groups, however it wasn't pushed onto people so they may not have known the late bookings were an option. One group reported that they treated the Early Bird Booking Deadline as their internal final deadline and another reported that they would accept bookings right up to the camp starting as long as the young person paid what they owed. 
\begin{table}[h]
    \centering
    {\RaggedRight
    \begin{tabular}{p{0.3\textwidth} p{0.5\textwidth}}
    \textbf{Date} & \textbf{Event}\\
    \hline
    \hline
    27 January 2023 & Bookings Open\\
    \hline
    12 April 2023 & Early Bird Booking Deadline\\
    \hline
    26 May 2023 & Final Booking Deadline\\
    \hline
    10 June 2023 & Booking Content Deadline\\
    & Refund Request Deadline (ad-hoc)\\
    \hline
    22 July 2023 & Late Booking Deadline\\
    \hline
    12 August 2023 & Very Late \& On-The-Door Booking Deadline\\
    \hline
    \end{tabular}
    } % end of rr     
    \caption{Internal Booking Timeline}
    \label{tab:booking-internal-timeline}
\end{table}

The refund deadline was added in an ad-hoc manner. This was due to the number of people wanting refunds for individuals coming up to the final booking deadline. The refund deadline was written into the payment policy and a second version was published on 24 May 2023.\\

Ultimately, not closing bookings proved valuable as a number of additional volunteers were recruited at DF camp to come and support the MEST-UP provision. These people paid the highest amount to come, the very late booking price, which supported us to hit our booking income target.
