\chapter{Pricing}
After developing the booking timeline and deciding about the expanded age ranges, we were able to decide on pricing for the camp.\\

Woodcraft Folk is committed to working to reduce barriers towards Volunteering. One such barrier, Venturer Camp presented a perfect test ground for - is the financial commitment to come to a camp. This resulted in us having the following pricing structure.

\begin{table}[h]
    \centering
    {\RaggedRight
    \begin{tabular}{p{0.2\textwidth} p{0.2\textwidth} p{0.2\textwidth} p{0.3\textwidth}}
    \textbf{Before} & \textbf{Age Bracket} & \textbf{Whole Camp} & \textbf{1 night}\\
    \hline
    \hline
    \multirow{2}{*}{26 May 2023} & Under 18 & \pounds150 & \pounds21.50\\
    \cline{2-4}
    & 18 and over & \pounds50 & \pounds7.50\\
    \hline
    \multirow{2}{*}{22 July 2023} & Under 18 & \pounds225 & \pounds32.25\\
    \cline{2-4}
    & 18 and over & \pounds75 & \pounds11.25\\
    \hline
    \multirow{2}{*}{12 August 2023} & Under 18 & \pounds300 & \pounds43\\
    \cline{2-4}
    & 18 and over & \pounds100 & \pounds15\\
    \hline
    \end{tabular}
    } % end of rr     
    \caption{Pricing Structure based on 1-person figures}
\end{table}
We made the decision that all those attending the camp who are aged 18 and over would be attending as a volunteer, and as such we would recognise their contribution by charging them a third of the participant cost. 

\section{Under-18 Volunteer Priced Places}
Due to the enlarged age ranges for Venturer Camp 2023, we also wanted to ensure those who could technically come as participants had the opportunity to volunteer without paying the (higher) participant price.\\

This desire led to the creation of the Under 18 Volunteer Price Scheme whereby a young person aged 16 or 17 could apply for a volunteer priced place if they were at the camp primarily as a volunteer. The scheme required a few things of the young person before the price reduction could be allocated: 
\begin{enumerate}
    \item have begun the process of obtaining a Enhanced DBS (or membership of the PVG scheme if based in Scotland);
    \item be registered as a member of Woodcraft Folk and have paid their membership fee;
    \item have submitted references (this will normally have been done as part of becoming a member of Woodcraft Folk); and 
    \item have spoken to the relevant team leader about the role and a volunteer role description has been produced (this should be included with the application).
\end{enumerate}
This scheme was widely publicised, and despite this - we only had approximately 5 people take part in it. The roles they took on ranged from stewarding to centre coordinator to cafe \& special diets kitchen assistant.\\

There were a number of young people who had paid the participant price who attended to volunteer. These young people coordinated a centre as a group. They made the decision to pay the participant price as they also engaged in some other programme. For future events, it might be worth having an intermediary pricing point for those young people who are volunteering some of the time and also participating at other times. 
