\chapter{Finding A Suitable Site}
For Venturer Camp 2023, the decision of what site to use was perhaps easier than in previous years. The accelerated timeline for the project meant that we would have had great difficulty finding a suitable site for Venturer Camp (thinking about infrastructure requirements on the site, transport links to the site, location in the country, etc).\\

Ultimately, we used Biblins Youth Campsite, which is owned by Forestry England and leased to Woodcraft Folk. Using a site which is managed by Woodcraft Folk, gives us greater flexibility and a level of quality assurance which would be unknown for other sites which we haven't worked with before.\\

From the feedback about the previous Venturer Camp's choice of site, also held at Biblins in 2019, you wouldn't have thought that we would use the site again. A large proportion of the campers commented that they were a very long distance from their village to the central area. These complaints were mostly from those camping on pitch 1 where they had to walk to Pitch 6 and 7 for the central programme. Since 2019, Biblins has undergone renovation works to relocate Camp Koodoo (its permanent camp) from Pitch 5 to adjacent to Pitch 1a. This resulted in us being able to centralise our central area onto pitches 4 and 5. We received little-to-no complaints about walking distance from villages to the central area, other than from those volunteers who would be in the central area up until meal times who would have to return to their village, collect food and then get straight back to the central area to finish programme delivery. This issue was quickly rectified, however, by the volunteers getting food delivered from their village to the central area. \\

For many months, the Coordination team had very little contact with the Biblins Staff Team; however, as camp approached, we had more contact with the team to gain information about the workings of the site, infrastructure on site and get copies of their policies and procedures which we would potentially need to implement while on site.\\

During the event itself, the Coordinator and Project Staff Team worked closely with the Biblins Staff Team, which enabled clear communication about issues and matters which arrose on site such as The Spill, access to the Bunkhouse Basement Storage and Adventurous activities, including a major change of plans to the Canoeing. \\

Having direct contact with the Biblins Staff Team proved invaluable and made the event considerably easier to organise.
