\chapter{Finance}
The finances for Venturer Camp 2023 were overseen by the Head of Resources at Woodcraft Folk with assistance and knowledge given from the Venturer Camp Treasurer and Coordinator. The decision to manage the finances like this came about from not having anyone in the treasurer post at the start of the project so the Coordinator and HoR began managing the finances themselves, then once a treasurer was appointed this felt like the simplest option. \\

The management of finances through the Woodcraft Folk systems had a number of benefits and drawbacks. The most notable benefit was that it was all dealt with for us (``us'' being the Core Team), with trained professionals managing the day to day running of the finance. The Treasurer was able to support by approving expenses and invoice payments as well as doing the first level of chasing for payments, later levels of chasing were done by the HoR.\\

One of the significant drawbacks of using the very established Woodcraft Folk finance system is that it is already set up very firmly. The Venturer Camp team's budget lines didn't match the central monitoring system, and this made our lives much more difficult when reviewing payments into and out of the account in order to monitor how much was being spent in each category. This was further exacerbated by the fact that the finance monitoring tools (a series of Google Sheets) were set up such that they required a great level of understanding to be able to read them. This resulted in large amounts of confusion amongst those people who had to read them and understand them. \\

Another significant drawback of using the Woodcraft Folk finance system was that quite often transactions were ``mis-coded'' within the system. This resulted in transactions erroneously appearing on the monitoring spreadsheet, or not appearing altogether - leading us to believe we hadn't spent as much as we in fact had. 

\section{Budget}
The first budget for Venturer Camp 2023 was drawn up by Woodcraft's Chief Executive using figures from Venturer Camp 2019 and Common Ground International Camp 2022 to influence expected expenditure for 2023. Throughout the project, minor alterations were made to the budget, mostly to reflect the change in expected income due to fundraising income being lower than initially expected.\\

Due to the above mentioned issues with income and expenditure coding within the Woodcraft Folk finance systems, and the fact that they do not line up with our budget lines - we do not have a final breakdown of expected vs actual for our budget.\\

Shown below is the Venturer Camp 2023 budget, compared to the Venturer Camp 2019 actual expenditure. 

