\chapter{Structure of the Week}

Most days in the week followed a similar structure, alternating between a chill night and a big night. There were overarching mini-themes which the big night's dress up themes related to. 

{\RaggedRight \centering
\begin{longtable}{p{0.15\textwidth} p{0.25\textwidth} p{0.25\textwidth} p{0.2\textwidth}}
 & \textbf{Afternoon} & \textbf{Evening} & \textbf{Mini Theme} \\ 
\hline
\endhead

\multicolumn{3}{r}{\footnotesize\itshape continued on next page}\\
\endfoot 

\endlastfoot

Saturday 5 & Arrivals & Opening video and Luna (Venturer drag queen) ABBA party & None (mythology in general) \\
\hline
Sunday 6 & Hiroshima Day focus in centres & Chill in villages & European Mythology \\
\hline
Monday 7 & Centres & Ceilidh & European Mythology \\
\hline
Tuesday 8 & Centres & Chill in villages & Ancient Mythology \\
\hline
Wednesday 9 & Wide game & Merry Moot, hosted by Luna & Ancient Mythology \\
\hline
Thursday 10 & AGM & Chill in villages, also Activism Talk Show and Venturer Committee election results & World Mythology \\
\hline
Friday 11 & Centres & Closing video and Hunny Buzz (band) & World Mythology \\
\hline
Saturday 12 & Departures &  & \\
\hline

\caption{Week's Structure at Venturer Camp 2023}
\end{longtable}
}% end of \RaggedRight

\section{Woodcraft Folk's Annual General Meeting}
A decision was taken by the General Council to host Woodcraft Folk's 2023 AGM at Venturer Camp, on Thursday afternoon. During the planning stages of the event, there were concerns that this would add an additional workload to the Venturer Camp team however these concerns were speculative and nothing came of them.\\

The planning and delivery of the AGM was not managed at all by the Venturer Camp team, other than ensuring that the Main Marquee was available and that there was an internet connection available for the hybrid aspect of the AGM. However, being that the AGM was held at Venturer Camp - a number of the central team members were dragged into supporting the event. This detracted from the efforts which could be put into Venturer Camp itself. The major sacrifice for the success of the AGM was restricting Internet Access further than usual for the duration, ensuring that the connection was stable enough for a Zoom call.\\

From the Venturer Camp feedback, some people commented that they disliked having the AGM held at one of Woodcraft's large camps. This is a conversation which the General Council needs to have, not for discussion in this report. 
