\chapter{Roadshow}
The Roadshow for Venturer Camp 2023 was a series of sessions facilitated by various members of the core team at regional events around the country in late 2022 and early 2023. These sessions aimed to spread the word of what was happening, gather potential participant's thoughts on the programme and answer leaders' questions.\\

It was decided to run these sessions as they had been done for previous camps, with greater success than ours however. Each of the different sessions went differently to each other, with some being great successes and others being less successful.\\

After some conversations, it was decided that it would be best to `piggyback' off of other events in the Woodcraft Folk calendar, rather than run our own events - due to the administrative \& financial impacts of running our own events. A session plan was devised by Woodcraft Folk's Chief Executive, which was designed with a number of sub-sessions in mind, so each Roadshow could be tailored to the audience, and time requirements.\\

The first roadshow was held in Scotland at their Scottish Gathering. This was a successful roadshow, probably due to the cohesive nature of the Scottish Nation in Woodcraft, and how core their Gathering is to their operations. This resulted in a large turnout of both young people and volunteers. The young people also re-wrote lyrics to a song which featured as part of an advert in the Venturer Camp news!\\

The roadshow then travelled to the Eastern Region for their first ever Eastern Region Venturers Fun day. This was facilitated by leaders based in the Eastern Region who were also on the Core Team. This was a successful event, mostly due to the fact that the target audience were present and the fact that the coordination team were experienced leaders who were able to take a session plan and engage young people \& adults in it.\\

The next stop for the Roadshow was the London Regional Gathering. This being a large event naturally meant that the Venturer Camp roadshow would be a smaller component than it was at either of its previous stops. Again, this was a successful event - gathering thoughts on programme activities from the young people in attendance and answering leaders' questions.\\

The Roadshow continued its journey south in the country to the South East Regional Gathering. This event was the least successful roadshow where any content was actually delivered. The event wasn't successful, due to the low number of attendees as well as the poor communications around the SE Gathering \& Venturer Camp roadshow. The low number of attendees, who were mostly adults, meant that the sessions designed to get participants talking had to be adapted and run as sessions for the leaders, still hoping to gather useful information. \\

The final stop for the Roadshow was supposed to be the biggest, as it was being planned to run as its own event. The event planning had all gone well, and we had agreed facilitators to run the event. We had planned to use a Youth Hostel Meeting Room in Manchester, as Woodcraft Folk has an agreement whereby they can access these facilities for free. A booking form had been created and circulated to Venturer Leaders through social media and our website. Unfortunately no one had booked. A decision was taken within the Woodcraft Folk Senior Leadership Team to cancel this event. This decision was communicated to the venue however not to any of the Volunteers working on the project. This resulted in the sessions facilitator finding out the session had been cancelled on arrival at the venue. This communication failure demoralised the team and soured the end of what, until this point, had been a successful roadshow.\\

The division of Roadshows around the country felt alright for a Venturer Camp sized camp. For a larger camp, it may be more beneficial to target all the functional regions \& hold general open access sessions, depending on what you wish to gain from them. Holding a roadshow virtually was also discussed but never happened due to time constraints, this could be a valuable opportunity to take. Piggy-backing off other events worked well, as our plans fit this well. It is suggested to repeat this. Generally the Roadshows were well received, with young people and volunteers alike getting excited about Venturer Camp 2023!
