\chapter{Concordia}
Woodcraft Folk worked with the company Concordia to recruit a team of international volunteers. This was the first time that Woodcraft has worked with Concordia and as such there were a number of teething difficulties.\\

A representative from Concordia visited the site in March 2023 to conduct a Health \& Safety audit. As part of this, the decision was made that the Burrow would act as a base for the Concordia team. This decision was not effectively communicated to the team at the time as until this point, it had been vaguely agreed that the core team would have access to the burrow as a place to sleep with better beds and a small kitchenette which the team could use to reheat food should they require this.\\

Concordia managed the recruitment of volunteers. While this saved time for the Venturer Camp team, it proved challenging to get this information out of Concordia. Specifically, their dietary requirements and any access needs were not communicated until after the standard booking deadline and one volunteer's information not being shared until days before the first members of the team were on site. In the end, we had nine volunteers, who all arrived in the country and were helpful with some tasks they were assigned. \\

In the lead up to the event, Woodcraft Folk's Programme Manager made repeated attempts to gain direct contact with the volunteers themselves however Concordia were reluctant to divulge the volunteers phone numbers. Ultimately, however, the Programme Manager was successful in gaining contact with the team. This allowed limited information to be shared with the volunteers. Unfortunately, this information came too late for many of the volunteers who had already packed and were unable to bring suitable clothing or prepare for their time at Venturer Camp. This led to a decreased spirit amongst the team and a general reluctance to do things.\\

Due to the lack of communication with the volunteer team in advance of the camp, no expectations were able to be set from Woodcrafts side. This led to a very harsh reality on the first night where we had to put the team up in tents rather than the burrow. Whilst the team did have suitable tents and sleeping mats provided from Biblins and the room of strategic requirement, a number of them did not bring suitable clothing for that night. The volunteer team also had the expectation that they would have more time off during the event. This led to lots of disappointment when they couldn't go off site to a Pub as they were needed to support other activities on site. \\

On-Site the two Centres ESC Volunteers were tasked with supporting the engagement of the Concordia volunteers. The two volunteers had training sessions with the Concordia staff team as well as the WCF Programmes Manager. Unfortunately, on site, the two ESC volunteers were not able to support the Concordia volunteers effectively which further led to low spirits within the international volunteers.\\

During Working Week, camp itself and takedown, the Concordia volunteers needed to be told exactly what to do and when. As this was their first experience of Woodcraft Folk and the way we camp, and for many of them - their first experience in a camp setting, they were unable to take initiative or move on to another task once what they were doing had been completed. This resulted in some confusion for them and frustration for the Woodcraft volunteers \& staff when the Concordia team wouldn't show up or they would not engage with changed plans, which unfortunately happened numerous times.\\

Due to an administrative error when reviewing the draft contract from Concordia within Woodcraft Folk, the Concordia volunteers were scheduled to arrive on Tuesday 1 August and depart on Monday 21 August. This error led to us having to put them in tents the first night they were on site. Luckily, we were able to provide this equipment for them, however the tents were not treated particularly well. Many of the doors were left open during the days following their use, when it rained heavily, hence we couldn't take them down. When the tents were finally taken down, they were thrown in a heap rather than being packed back into their bags. These actions resulted in the exhausted Woodcraft volunteer takedown team needing to do extra work to clear up after the Concordia team.
The date the Concordia team was booked to depart was later than that originally advertised to the Coordination team of the camp. This resulted in some confusion amongst both the Woodcraft Volunteers and Concordia team. Ultimately, all the members of the Concordia team paid to change their flights / booked new flights to depart on either the 16 or 17 August. \\

The volunteers showed they had the independence to navigate trips to shops and pubs (neither of which are particularly close to site), but did not apply this to tasks on site and often did these things when they were meant to be on shift either at the time or early the next morning when they often didn't show up because they were still asleep.\\

We were very clear in all our communications about the camp (including the info packs we sent Concordia) that there would not be much signal or Wifi on site. However Concordia failed to pass this info on, and as a consequence we felt we had to share the wifi with the volunteers so they could keep in touch with friends and family. This meant they were often hanging around the cabin to use the wifi, making it slow for people needing it to make the camp happen/run the site, and bothering other volunteers/staff for the password when we had to change it so the staff on site could do their jobs. \\

The volunteers were very helpful when it came to putting up lots of 5x10m marquees in working week, and also some of them supported other jobs really well e.g helping the shuttle bus volunteers on arrivals and departures days, some stewarding shifts etc. However overall, it was more work for us to manage them and give them things to do, plus paying for their food and board, than the little work they did on site. This is partly due to lack of planning and understanding on our part, and partly due to Concordia not delivering what they said they would in terms of giving us and the participants the information we needed.\\

It would not be recommended to work with Concordia again for the reasons outlined above. Should Woodcraft Folk decide to work with them again, written assurances should need to be provided to the Camp Coordinator / Project Manager that the issues outlined above will be addressed and resolved to the satisfaction of Woodcraft Folk
