\chapter{Staff Support}
Woodcraft Folk's Events Assistant was able to devote the majority of her 14 weekly hours to Venturer Camp from November 2022 until December 2023. This time was used to book major infrastructure, do some of the event administration, communications and support the Production and Programme teams, among other things. This role is managed by the Programme Manager, who also contributed some time in the last few months leading up to the event and on site. \\

The CEO of Woodcraft Folk put lots of time into this event from its conception, supporting the Coordinator and the programme team, leading on risk management and safeguarding both in the run up and on site, as well as helping with other things.\\

On site the Events Assistant, Programme Manager and CEO took on coordinator shifts along with the Coordinator and occasionally other volunteers. The CEO took on the majority of the safeguarding shifts with support from one volunteer and also the Head of Memberships \& Programmes (and Woodcraft's Designated Safeguarding Lead) at the very end of camp. With more than one volunteer coordinator and a volunteer safeguarding officer this level of support on site would not be needed.\\

From early May until the camp, the membership team supported us by doing membership and DBS checks, chasing those without them and supporting these people to sort it. This saved the camp team a lot of time compared to Common Ground when the Camp Assistant (staff administrator job role) did much of this. \\

The Head of Resources helped us set up accounts with food suppliers, and the finance team helped us pay invoices and expense individuals. Woodcraft's Fundraiser (Individual \& Legacy Giving) raised £6000 from the Christmas Challenge and this enabled us to offer an access fund to people who couldn't afford the full camp fee.\\

This camp had a lot more staff support than Venturer Camps have done in the past, with the creation of the new Events Assistant role and also the accelerated timeline for planning the camp meaning the team needed more support. It's also thought that since the pandemic volunteering attitudes, knowledge and experience have changed quite a lot, making it harder to recruit people. Some level of staff support is essential, with the Events Assistant role aiding continuity of knowledge between events and support from the experts on finance, membership and safeguarding. Hopefully future camps will not need this level of support, with a longer planning timeline and more young people moving into volunteer roles with experience developed from this camp, Common Ground and Camp 100.
