\chapter{Introduction to the Evaluation}
This Final Report \& Evaluation of Venturer Camp 2023 has been primarily compiled by Thomas Boxall, Venturer Camp 2023 Coordinator (Volunteer), and Millie Burgh, Woodcraft Folk Events Assistant (Staff).\\

Every effort has been made to ensure that this report is as accurate and representative of all teams as possible. However, there may be times where this was not possible. All data referenced throughout this evaluation is available on request. Please contact the Camp Coordinator should you have any questions or wish to seek clarification on anything.

\section{Methods Used}
Opinions and Thoughts from the wider coordination team were gathered through a series of interviews conducted by the Camp Coordinator and Events Assistant. \\

Feedback from participants was gathered during the event itself through a Workshop run on a village level. Not all villages submitted notes from their workshop, so participant evaluations may not be representative of all participants on site. \\

All Volunteers involved in the project were invited to complete a Google Forms questionnaire after camp where they could give feedback. As expected with a survey like this, not all volunteers have responded and those who have responded would fall at either end of the spectrum, either having lots of good things to say or lots of bad things. Conversations had with volunteers throughout the event have been included.
\begin{figure}[h]
    \centering
    \begin{tikzpicture}
        \pie[text=legend, color={blue!70,cyan!70,red!70,orange!50}]{10/First, 20/Second, 30/Third, 40/Fourth}
    \end{tikzpicture}
    \caption{Caption}
    
\end{figure}