\chapter{Bookings}
Bookings opened on the 27th January at 6pm. There have been a number of applications to book so far.

\section{Booking System}
After a small amount of research and debate, it was decided that the best booking system to use would be a modified version of Ralph's Common Ground booking system.\\

A number of modifications have been made by Ralph, including a significant security increase however fundamentally it is the same system we used for Common Ground.\\

A \href{https://venturercamp.org.uk/wp-content/uploads/2023/01/booking-handbook-v1.pdf}{booking handbook} has been produced detailing how to use the system. 

\section{Booking Timeline}
\begin{table}[H]
    \begin{tabularx}{\textwidth}{XX}
        \textbf{Date} & \textbf{Booking Event}\\
        \hline
        \hline
        27th January 2023 & Bookings Open\\
        \hline
        12th April 2023 & Early Bird Booking Deadline\\
        \hline
        26th May 2023 & Final Booking Deadline\\
        \hline
        22nd July 2023 & Late Booking Deadline\\
        \hline
    \end{tabularx}
    \caption{Booking Timeline}
\end{table}
The Final booking Deadline is being advertised as the final opportunity to book. In reality, we will allow bookings right up until the end of camp, however we have stressed in the \href{https://venturercamp.org.uk/wp-content/uploads/2023/01/payment-policy-v1.pdf}{payment policy} that after 10th June 2023 food orders will have been placed and we cannot guarantee that dietary needs can be met after this date. Until we reach the final booking deadline, we will not be outwardly advertising the not-closing nature of the bookings. 

\section{Early Bird Booking Deadline}
If a booking and deposit is receive before the early bird booking deadline, the participants booked will receive a free, limited edition t-shirt. This will be a limited edition design, specifically for those who booked before the early bird booking deadline. There is no financial discount for booking before 12th April 2023.