\chapter{Budget \& Finance}

Before we were able to recruit a volunteer treasurer, Debs drew up a budget. This was approved as part of the budget presented to General Council in December 2022.\\

The budget takes into considerations costs from Venturer Camp in 2019 as well as costs from Common Ground and inflation. There have been a number of minor revisions to the budget to include additional categories as the camp planning and planning for events leading up to the camp have progressed.

The budget has been designed such that we should break even.\\

The current budget is designed for 400 participants, 300 of those paying full price. The other 100 will be volunteer places who will be paying the reduced volunteer price.\\

\section{Pricing}
The table below outlines the pricing strategy for Venturer Camp 2023. More information on bookings can be found in the Booking section.
\begin{table}[H]
    \begin{tabularx}{\textwidth}{XXXX}
        \textbf{Before} & \textbf{Age Bracket} & \textbf{Whole Camp PPP} & \textbf{1 night PPP}\\
        \hline
        \hline
        \multirow{2}{*}{26th May 2023} & Under 18 & £150 & £21.50\\
        \cline{2-4}
         & 18 and over & £50 & £7.50\\
        \hline
        \multirow{2}{*}{22nd July 2023} & Under 18 & £225 & £32.25\\
        \cline{2-4}
         & 18 and over & £75 & £11.25\\
        \hline
        \multirow{2}{*}{12th August 2023} & Under 18 & £300 & £43\\
        \cline{2-4}
         & 18 and over & £100 & £15\\
        \hline
    \end{tabularx}
    \caption{Pricing breakdown by date, age, and duration at camp}
\end{table}

Following the General Council discussion on financial inclusion it was decided to pilot reduced fees for voluneers at Venturer Camp for the following reasons
\begin{itemize}
    \item Venturer Camp provides a programme for Venturers;
    \item Venturer Camp does not provide a family camp experience, unlike other Woodcraft Folk events;
    \item Many volunteers at Venturer Camp are young people who are not salaried and would significantly miss out financially by choosing to volunteer to attend.
\end{itemize}

An access fund will be in place to reduce any financial barriers experienced by Venturers. This is being supported by some of the proceeds from the Big Give Christmas Challenge.