\chapter{Team Update}
This section will provide an update on how the coordinating team is structured, where additional support would be needed, a request for General Council and some information about meetings \& communications between the team as this may be useful to other active/ future projects.
\section{Team Size}
As of the first draft of this paper, the team structure is as follows.\\
\textit{Please Note: this may not be accurate as these are the figures which the Camp Coordinator has.}
\begin{table}[H]
    \begin{tabularx}{\textwidth}{lXX}
        \textbf{Team Name} & \textbf{Core Volunteers} & \textbf{Supporting Volunteers} \\
        \hline
        \hline
        Camp Coordinator & 1 & 0\\
        \hline
        Programme Team & 2 & 4\\
        \hline
        Site Services/ Production Team & 3 & 0\\
        \hline
        Communications Team & 0 & 0\\
        \hline
        Food Team & 3 & 3 \\
        \hline
        Cafe \& Allergy Kitchen Team & 2 & 2 \\
        \hline
        Volunteer Support Team & 2 & 0\\
        \hline
        Finance Team & 1 & 0\\
        \hline
        Admin Team & 0 & 0\\
        \hline
        Transport & 2 & 0\\
        \hline
        Sustainability \& Environment & 3 & 0\\
        \hline
        Head Stewards & 1 & -\\
        \hline
        Booking System Development & 1 & 0\\
        \hline
    \end{tabularx}
    \caption{Volunteer team breakdown}
\end{table}

We also have the support of a number of members of staff: Millie is providing support to a number of teams; Debs is providing support to the health \& safety paperwork; Felix is providing some support to the programme team with local contacts; and Richard is providing support to the finance team.

Contact information for the volunteer team is available through \href{https://venturercamp.org.uk/contact/}{our website}.

\section{Recruitment Needs}
As you may be able to see from the table above, there are a few gaps in volunteer numbers. There are a number of roles where the camp would benefit from some additional support. 

The full list of roles we are actively recruiting for can be found on \href{https://venturercamp.org.uk/get-involved/}{our website}.

It would be great if General Council can use their contacts or people in their district who want to get more involved with Woodcraft to promote the voluntary opportunities available.

\section{Meetings}
The core team have been meeting monthly for a check-in style meeting with a business agenda attached. This is something which DF Committee do and it was felt that this approach would give a good chance for issues to be reported earlier and support can be easily sought. The meetings take place on alternating evenings within the week on Zoom.\\

Attendance to the meeting is good and teams provide an update as to where they are. Through this support needs and next steps can be identified.

\section{Communications}
The whole team are using Discord to communicate. This has been configured such that there are areas for all volunteers and areas where the core team can discuss things separately. Each team (for example, food) have their own space where they can create text \& voice channels. Teams have been invited to join the server where the `coordinators' for that role are able to communicate with the `supporting volunteers'. \\

The whole team has engaged with this really well and, for the most part, are active on it. Using a platform of this nature (channel based discussion) has had a really positive impact on the coordination of the camp and has reduced the need for emails to almost none.\\

The team have a folder within the \texttt{Events - Current \& Historical} Shared Drive where they store their data.\\