\chapter{Roadshow}
Members of the Venturer Camp team will be attending a number of events around the country to deliver sessions about Venturer Camp.
\begin{table}[H]
    \centering
    \begin{tabularx}{\textwidth}{XX}
        \textbf{Location} & \textbf{Date}\\
        \hline
        \hline
        Scotland & 28th January\\
        \hline
        London (London Region Gathering) & 5th March\\
        \hline
        Brighton (SE Regional Gathering) & 18th March\\
        \hline
        Manchester (Venturer Camp Roadshow Event) & 25th March\\
        \hline
        Online & TBD\\
        \hline
    \end{tabularx}
    \caption{Roadshow dates}
\end{table}

The content covered in the roadshow will range from an introduction to the camp aimed at Venturers \& leaders; camplife \& camp programme; getting involved; and a Q\&A session. (Not all locations will have the same sessions offered due to time constraints).

\chapter{Pre-Camp}
Pre-Camp will be hosted as a series of online events, culminating in an on-site weekend in early July which will not be open to all.
\section{Virtual Events}
The majority of the pre-camp events will take place as virtual events on Zoom throughout late April, May and June. These sessions will be hosted on Zoom and will take place on different nights of the week.\\

Slides and any other materials used in sessions will be made available on the Venturer Camp website ahead of the session. Some sessions may be recorded and the recordings published after the session.\\

In-detail planning is yet to begin for the sessions. Content will be published to our social media and website once we have dates for sessions.

\section{On-site event}
We have a pitch at Biblins booked from the 30th June to 2nd July. This will give the team a chance to meet the staff on site, visit the site and work out logistics on site.\\

We will be inviting one leader and up-to one Venturer from each booked delegation to meet the other people in their villages.