\chapter{Payment Policy for Groups}

\section{Standard Camp Fees}
The standard camp fees are outlined in the table below.
\begin{table}[H]
    \centering   
    \begin{tabularx}{0.9\textwidth}{XXX}
        \textbf{Age Bracket} & \textbf{Whole camp price per person} & \textbf{1 night per person} \\
        \hline
        \hline
        Under 18 & £150 & £21.50\\
        \hline
        18 and over & £50 & £7.50\\
        \hline
    \end{tabularx}
    \caption{Standard camp price breakdown for all ages}
\end{table}

\section{Early Bird Offer}
If your booking \& deposit is received before 12th April 2023, participants will be eligible for a free, limited edition Venturer Camp 2023 t-shirt. Any participants added after 12th April 2023 will not be eligible.\\[1em]
There is no financial discount for booking before 12th April 2023.

\section{Payment}
All payments should be made \textbf{using your unique booking reference number} to:\\
\textbf{Bank} Unity Trust plc

\textbf{Account Name} Woodcraft Folk  

\textbf{Account Number} 20392756   

\textbf{Sort Code}  60-83-01  

\textbf{Bank Address} 4 Brindey Place, Birmingham, B1 2JB  

\textbf{Swift Code (BIC)} NWBKGB2L  

\textbf{IBAN Number} GB93NWBK60023571418024  

\subsection{Deposits}
Your group booking is secure after you have paid 50\% of your delegation costs. The deposit is non-refundable but will be taken out of your group's remaining balance.

\subsection{Paying the remaining balance}
You need to have paid the remaining balance for your group by 26th May 2023 but please make payments as soon as your group can afford to. The funds raised will go towards making the camp sound, look, taste and smell even better.

We will not be allowing any groups access to camp if their fees have not been paid in full upfront. This is in fairness to all the other delegations who have paid by the deadline.

\section{Late Bookings}
We may not be in a position to take bookings after 26th May 2023 and reserve the right to increase the camp fee after this date as shown in the table below. From 26th May, the fees have to be paid on booking, upfront in one instalment.

We reserve the right to not accept entire new delegations after 26th May 2023.
\begin{table}[H]
    \centering   
    \begin{tabularx}{0.9\textwidth}{XXX}
        \textbf{Age Bracket} & \textbf{Whole camp price per person} & \textbf{1 night per person} \\
        \hline
        \hline
        Under 18 & £225 & £32.25\\
        \hline
        18 and over & £75 & £11.25\\
        \hline
    \end{tabularx}
    \caption{Late booking price breakdown for all ages}
\end{table}

By 10th June 2023, the food order will have been placed. We cannot guarantee that dietary needs can be met after this time.

You will also need to ensure that DBS/ PVG checks are in place for all participants aged 18 or over. We will not be allowing access to camp for anyone without a valid DBS/ PVG.

\section{Very Late Booking \& On the door}
After the 22nd July 2023, we may not be in a position to take bookings and reserve the right to further increase the camp fee after this date as shown in the table below. From 22nd July 2023, the fees have to be paid on booking, upfront in one instalment. 
\begin{table}[H]
    \centering   
    \begin{tabularx}{0.9\textwidth}{XXX}
        \textbf{Age Bracket} & \textbf{Whole camp price per person} & \textbf{1 night per person} \\
        \hline
        \hline
        Under 18 & £300 & £43\\
        \hline
        18 and over & £100 & £15\\
        \hline
    \end{tabularx}
    \caption{Very late booking price breakdown for all ages}
\end{table}

\section{Cooling-off period}
There is a cooling-off period of 14 days from the time when you first pay the deposit to change your mind. In this time period, you are eligible for a full refund and your group does not have to give a reason for the cancellation.

\section{Refunds}
The camp fees generally go towards upfront costs.  For this reason, we regret to say we are unable to offer refunds to groups who withdraw prior to attending.\\[1em]
In the unlikely event that you book onto camp and your group is then unable to take part, please first try to find replacement participants and group leaders. This is to avoid disappointing any young people who have already been expecting to attend. Then contact \href{mailto:info@venturercamp.org.uk}{\texttt{info@venturercamp.org.uk}} where our team will make every effort to support you in finding a satisfactory solution. There is guidance available for fundraising, and for accessing camping equipment. You are important to us and we want to enable as many groups as possible to attend.\\[1em]
If during camp you are unsatisfied with the experience, please contact camp management on site, at the earliest opportunity. We want everyone to enjoy their experience and will actively work with you to resolve the issue. We regret to say that at the time of the camp, the expense has already been incurred and we are unable to offer refunds. Please use the camp procedures or Woodcraft Folk complaints policy for raising issues.

