\chapter{Payment Policy for Individual participants}
Participation at camp is encouraged as part of a group. This is for your social, safety and financial benefit. Participants are likely to have a much richer experience attending with a group. However, participants aged 18 or above can choose to book independently if there is no alternative.\\[1em]
Members attending the camp who are aged 18 and above should be taking on a significant role, whether this be on a local village, or central level. The Venturer Camp 2023 team reserves the right to reject a booking application where there is not a significant commitment on camp demonstrated.

\section{Standard Camp Fees}
The table below shows the camp fees for participants aged 18 or over.

Any participant attending Venturer Camp 2023 will need to be a fully-paid-up member of Woodcraft Folk. Participants aged 18 and above will need to hold a valid DBS/ PVG check.
\begin{table}[H]
    \centering   
    \begin{tabularx}{0.9\textwidth}{XXX}
        \textbf{Age Bracket} & \textbf{Whole camp price per person} & \textbf{1 night per person} \\
        \hline
        \hline
        18 and over & £50 & £7.50\\
        \hline
    \end{tabularx}
    \caption{Standard camp price breakdown for over 18s}
\end{table}

\subsection{Early Bird Offer}
If your booking \& deposit is received before 12th April 2023, you will be eligible for a free, limited edition Venturer Camp 2023 t-shirt.\\[1em]
There is no financial discount for booking before 12th April 2023.

\section{Payment}
If you have difficulties paying, please contact \href{mailto:info@venturercamp.org.uk}{\texttt{info@venturercamp.org.uk}} and we will make every effort to allow you to pay by standing order.
All payments should be made \textbf{using your unique booking reference number} to:\\
\textbf{Bank} Unity Trust plc

\textbf{Account Name} Woodcraft Folk  

\textbf{Account Number} 20392756   

\textbf{Sort Code}  60-83-01  

\textbf{Bank Address} 4 Brindey Place, Birmingham, B1 2JB  

\textbf{Swift Code (BIC)} NWBKGB2L  

\textbf{IBAN Number} GB93NWBK60023571418024  

\subsection{Deposits}
Your booking is secure after you have paid 50\% of your camp fee.\\[1em]
The deposit is non-refundable but will be taken out of your remaining balance.


\subsection{Paying the remaining balance}
You need to have paid the remaining balance by 26th May 2023.

We will not be allowing any people access to camp if their fees have not been paid in full upfront. This is in fairness to all the other delegations who have paid by the deadline.

\section{Late Bookings}
We may not be in a position to take bookings after 26th May 2023 and reserve the right to increase the camp fee after this date as shown in the table below. From 26th May, the fees have to be paid on booking, upfront in one instalment.
\begin{table}[H]
    \centering   
    \begin{tabularx}{0.9\textwidth}{XXX}
        \textbf{Age Bracket} & \textbf{Whole camp price per person} & \textbf{1 night per person} \\
        \hline
        \hline
        18 and over & £75 & £11.25\\
        \hline
    \end{tabularx}
    \caption{Late booking price breakdown for over 18s}
\end{table}
By 10th June 2023, the food order will have been placed. We cannot guarantee that dietary needs can be met after this time. 

\section{Very Late Booking}
After the 22nd July 2023, we may not be in a position to take bookings and reserve the right to further increase the camp fee after this date as shown in the table below. From 22nd July 2023, the fees have to be paid on booking, upfront in one instalment. 
\begin{table}[H]
    \centering   
    \begin{tabularx}{0.9\textwidth}{XXX}
        \textbf{Age Bracket} & \textbf{Whole camp price per person} & \textbf{1 night per person} \\
        \hline
        \hline
        18 and over & £100 & £15\\
        \hline
    \end{tabularx}
    \caption{Very late booking price breakdown for over 18s}
\end{table}

\section{Cooling Off Period}
There is a cooling-off period of 14 days from the time when you first pay the deposit to change your mind. In this time period, you are eligible for a full refund and you do not have to give us a reason for your cancellation. 

\section{Refunds}
The camp fees generally go towards the camp infrastructure, food and other upfront costs.  For this reason, we regret to say we are unable to guarantee to offer refunds to anyone who withdraws. However we understand that losing a sum of money could put you in hardship. Therefore please speak to us at the earliest opportunity if you have payment difficulties. We want to help you with fundraising advice and with practicalities. Please contact us on \href{mailto:info@venturercamp.org.uk}{\texttt{info@venturercamp.org.uk}}. You will not be pressured into attending the camp if you don't want to.\\[1em] 
If during camp you have any problems, please contact camp management on site, at the earliest opportunity. We want everyone to enjoy their experience and will actively work with you to resolve the issue. We regret to say that at the time of the camp, the expense has already been incurred and we are unable to offer refunds. Please use the camp procedures or Woodcraft Folk complaints policy for raising issues.
